Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-08-16 Masterarbeit_Robotik_Pamuk.tex
Related Work 1.3 Papers read++

\bigskip \noindent \citeauthor{taccariEmbeddedRealTimeVirtualization2014} \cite{taccariEmbeddedRealTimeVirtualization2014}, \citeauthor{sandstromVirtualizationTechnologiesEmbedded2013} \cite{sandstromVirtualizationTechnologiesEmbedded2013}, and \citeauthor{guStateoftheArtSurveyRealTime2012} \cite{guStateoftheArtSurveyRealTime2012} all discuss and compare the current state-of-the-art in virtualization technologies on embedded real-time platforms.

highlighting similar advancements and challenges in their respective works.

\bigskip \noindent 
\citeauthor{garcia-vallsChallengesRealtimeVirtualization2014} \cite{garcia-vallsChallengesRealtimeVirtualization2014}

\citeauthor{cinqueVirtualizingMixedCriticalitySystems2022} \cite{cinqueVirtualizingMixedCriticalitySystems2022}

@@

\bigskip \noindent Virtualization offers the great benefit of reducing overall hardware costs, since all non-critical activities and real-time control tasks can run on the same hardware. \citeauthor{scordinoRealTimeVirtualizationIndustrial2020} \cite{scordinoRealTimeVirtualizationIndustrial2020} take advantage of this, but also address the challenge of interference on shared hardware resources, which can degrade real-time performance. In addition, \citeauthor{javierperezHowRealTime2022} \cite{javierperezHowRealTime2022} state that hardware-based PLCs are costly to maintain and lack the flexibility needed for modern, resource-intensive applications like Machine Learning (ML) or Artificial Intelligence (AI).

@@

\bigskip \noindent \citeauthor{broskyShieldedProcessorsGuaranteeing2003} \cite{broskyShieldedProcessorsGuaranteeing2003} report in their work about the shielded CPU model for enhancing real-time performance in symmetric multiprocessor systems. By dedicating one or more CPUs to high-priority processes and interrupts, the goal is to provide deterministic execution of real-time applications and interrupt responses. The authors mention that there is no user interface for setting process CPU affinity in the standard Linux, while there is one for setting interrupt CPU affinity via the \texttt{/proc/irq/*/smp\_affinity} files. These files were used in this masther's thesis. According to \citeauthor{broskyShieldedProcessorsGuaranteeing2003}, the shielded CPU model is especially useful for tasks that require guaranteed interrupt response times, very fast interrupt responses and high-frequency, deterministic execution.

@@

\bigskip \noindent \citeauthor{deoliveiraDemystifyingRealTimeLinux} \cite{deoliveiraDemystifyingRealTimeLinux} critique the traditional \texttt{cyclictest} tool used for measuring scheduling latency, highlighting its limitations due to its black-box approach and lack of theoretical grounding. This is the main reason why this tool was not used to measure the scheduling latency in this work. Instead, the \texttt{latency} tool was used,as was determined in Chapter \ref{sec:application_context}.

\bigskip \noindent \textcolor{red}{The paper titled “Real-Time Performance and Response Latency Measurements of Linux Kernels on Single-Board Computers” by George K. Adam from the CSLab Computer Systems Laboratory, University of Thessaly, investigates the real-time performance of Linux kernels with the PREEMPT\_RT patch on embedded devices like the BeagleBoard and Raspberry Pi1. The research focuses on measuring latencies in real-time applications at both user and kernel space using newly developed software modules tailored for these experiments2. The study highlights that the PREEMPT\_RT patch significantly improves the real-time performance of Linux kernels, reducing worst-case latencies to around 160 µs, making these systems more suitable for real-time applications3. The methodology involves response and periodic task models, and the results suggest that the proposed measurement approach can be applied to other Linux-based platforms4. The paper also discusses the challenges and solutions encountered during the experiments, emphasizing the importance of real-time capabilities in embedded systems for applications ranging from consumer electronics to industrial automation.}

@@

\bigskip \noindent \textcolor{red}{Title: How Real (Time) Are Virtual PLCs?1
Authors: Diogenes Javier Perez, Josef Waltl, Laurin Prenzel, Sebastian Steinhorst
This paper explores the concept of virtual programmable logic controllers (vPLCs) as a solution to the limitations of traditional hardware-based PLCs in industrial automation. The authors argue that hardware PLCs are costly to maintain and lack the flexibility and scalability needed for modern applications, especially those involving artificial intelligence and machine learning2. The proposed vPLC operates on a commercial off-the-shelf (COTS) server using a real-time hypervisor, which allows it to manage multiple virtual machines and handle resource-intensive tasks efficiently34.
The paper details the architecture of the vPLC, which includes a real-time operating system and a hypervisor to ensure low latency and deterministic behavior. The authors conducted various tests to compare the performance of vPLCs with traditional SoftPLCs, focusing on metrics such as cycle time, jitter, and response time. The results indicate that vPLCs can achieve performance on par with traditional PLCs for applications requiring response times below 10 milliseconds5. The study concludes that while further improvements are needed, vPLCs offer significant advantages in terms of flexibility, scalability, and cost-efficiency for future industrial systems6.}

>>>>

\bigskip \noindent \citeauthor{sandstromVirtualizationTechnologiesEmbedded2013} \cite{sandstromVirtualizationTechnologiesEmbedded2013}, and \citeauthor{taccariEmbeddedRealTimeVirtualization2014} \cite{taccariEmbeddedRealTimeVirtualization2014} and  discuss and compare the current state-of-the-art in virtualization technologies with a focus on embedded real-time platforms. The latter emphasizes, that research on real-time systems is focusing on virtualization and multicore scheduling and underlines that flexibility and cost are key metrics. Both works acknowledge the great benefits of virtualization, that is, reducing overall hardware costs, since all non-critical activities and real-time control tasks can run on the same hardware. In addition, \citeauthor{javierperezHowRealTime2022} \cite{javierperezHowRealTime2022} state that hardware-based Programmable Logic Controllers (PLCs) are costly to maintain and lack the flexibility needed for modern, resource-intensive applications like Machine Learning (ML) or Artificial Intelligence (AI).

\bigskip \noindent Despite the promising advantages of virtualization, one must be aware of the potential drawbacks of it, too. \citeauthor{guStateoftheArtSurveyRealTime2012} \cite{guStateoftheArtSurveyRealTime2012} highlight issues like lock-holder preemption and task-grain scheduling. \citeauthor{garcia-vallsChallengesRealtimeVirtualization2014} \cite{garcia-vallsChallengesRealtimeVirtualization2014} identify challenges in supporting real-time applications in the cloud, including resource management, quality of service guarantees, temporal and spatial isolation, and network performance. \citeauthor{scordinoRealTimeVirtualizationIndustrial2020} \cite{scordinoRealTimeVirtualizationIndustrial2020} address the challenge of interference on shared hardware resources, which can degrade real-time performance.

\bigskip \noindent
\citeauthor{cinqueVirtualizingMixedCriticalitySystems2022} \cite{cinqueVirtualizingMixedCriticalitySystems2022}

@@

@@

\bigskip \noindent \citeauthor{broskyShieldedProcessorsGuaranteeing2003} \cite{broskyShieldedProcessorsGuaranteeing2003} report in their work about the shielded CPU model for enhancing real-time performance in symmetric multiprocessor systems. By dedicating one or more CPUs to high-priority processes and interrupts, the goal is to provide deterministic execution of real-time applications and interrupt responses. The authors mention that there is no user interface for setting process CPU affinity in the standard Linux, while there is one for setting interrupt CPU affinity via the \texttt{/proc/irq/*/smp\_affinity} files. These files were used in this masther's thesis. According to the authors, the shielded CPU model is especially useful for tasks that require guaranteed interrupt response times, very fast interrupt responses and high-frequency, deterministic execution.

@@

\bigskip \noindent \citeauthor{deoliveiraDemystifyingRealTimeLinux} \cite{deoliveiraDemystifyingRealTimeLinux} critique the traditional \texttt{cyclictest} tool used for measuring scheduling latency, highlighting its limitations due to its black-box approach and lack of theoretical grounding. This is the main reason why this tool was not used to measure the scheduling latency in this work. Instead, the \texttt{latency} tool was used, as was determined in Chapter \ref{sec:application_context}.

@@
